The Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-09 ms.tex
3.3 update2

\begin{figure}
  \includegraphics[width=\columnwidth]{cooling.eps}
  \caption{\label{fig:cooling} Ratio of the rate of heating to radiative cooling, $\dot{q}_{\rm heat}/\dot{q}_{\rm cool}$, as a function of radius for each of our solutions (solid lines).  Shown for comparison with dashed lines is the ratio of the cooling to the local free-fall timescale $t_{\rm cool}/t_{\rm ff}$.  For high heating rates both ratios are approximately equal at the stagnation radius (marked with a square for each solution).  When $\dot{q}_{\rm heat}/\dot{q}_{\rm cool} \lesssim 1$ and $t_{\rm cool}/t_{\rm ff} \lesssim 10$ the flow will be susceptible to global and local thermal instability, respectively (e.g.,  \citealt{McCourt+12}).  {\bf BDM: change y axis labels to qdotheat/qdotcool, tcool/tff}.}
\end{figure}

@@

This section describes the results of our numerical calculations, which we use to study the range of plausible CNM properties and to assess the validity of the analytic expressions provided in the previous section.  Our results are summarized in Table \ref{table:models} and Figure XXX.  Cases for which $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|_{r_{\rm s}} < 1$ are marked as `thermally unstable', as are cases for which the stagnation radius become very large and could not be resolved, resulting in their calculations being terminated.

Figure~\ref{fig:profiles} shows profiles of the density $\rho(r)$,
temperature $T(r)$, and radial velocity $|v(r)|$, for the cusp
($\Gamma=0.8$) solutions within our grid.  As expected, the gas
density increases towards the SMBH $\rho\propto r^{-n}$ with
$n\simeq1$, i.e. shallower than the $-3/2$ power law for
Bondi accretion. This power law behavior does not extend
through all radii, however, as the gas density profile has a break coincident
with the location of the break in the stellar light profile ($\rb=100$
pc). The temperature profile is relatively flat at large radii, but
increases as $\propto 1/r^{k}$ interior to the sphere of influence,
where $k$ is smaller than 1--the power expected for virialized gas within the black hole sphere of influence.
The inwardly directed velocity increases towards the hole with a profile that is somewhat steeper than the local free-fall velocity $v \propto v_{\rm ff}\propto r^{-1/2}$.
% {\bf BDM: I made this up - in general we need
%   more explanation of what the plots are actually showing, with some
%   physical explanation.}
% AG -- things are not quite approaching Bondi on the inner grid. I
% don't have a good physical explanation yet...

Figure~\ref{fig:stag} shows our results for the
stagnation radius $r_{\rm s}$, expressed in ratio to the radius of the
SMBH sphere of influence $r_{\rm soi}$, with different colors showing
different values of $v_{w}$.  Cusp and core galaxies are marked with
square and triangles, respectively.

 We may also compare our numerical results $r_{\rm s}/r_{\rm
  soi}$ an be compared directly to our analytic estimate in equation
\ref{eq:stag_analytic}.  The solid and dashed black curves in  Figure
\ref{fig:stag} show the analytic results for $r_{\rm s}/r_{\rm soi}$.
The good agreement provides a useful check of the numerical
results. Note that the analytic curves implicitly assume a density
slope, $n$ at $\rs$, which we have fixed to be 1 (0.5) for the solid
(dashed) curve. For small $\vw/\sigma$ this assumption breaks down.

For $\vw/\sigma \gg 1$ the value $\rs/\rsoi$ does not depend on break
radius, $r_b$. On the other hand for $\vw/\sigma \simeq 1$, $\rb$ does
have an effect. Notice that near where the solid analytic curve
diverges there are three green square, one over the other. These
points correspond to models with the same $\Mbh (10^7 \Msun)$, $\vw
(300 {\rm km/s})$, and $\Gamma (0.8)$, but different values of the
break radius: from top to bottom 50 pc, 100 pc, and 400 pc.  
%% AG: Describe conservation checks to additionally validate the results.

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
    $r_{s}$ (in units of the radius of the sphere of influence $r_{\rm
      soi} = GM_{\bullet}/\sigma^{2}$) for galaxies in our sample as a
    function of the ratio of the effective wind heating rate $v_{w}$
    to the stellar velocity dispersion $\sigma$.  Green, orange, and
    blue symbols represent $v_{w} =$ 300, 600, and 1200 km s$^{-1}$,
    respectively.  Squares correspond to cusp galaxies, while
    triangles correspond to cores. The black curves correspond to the
    analytic prediction from Equation~\eqref{stag_analytic}. The solid
    (dashed) curve is the correponds to $\Gamma=0.8$ and $n=1$
    ($\Gamma=0.1$ and $n=0.5$.}
\end{figure}

>>>>

@@

The results of our numerical calculations are uses to study the range of plausible CNM properties and to assess the validity of the analytic expressions provided in the previous section.  Our results are summarized in Table \ref{table:models} and Figure XXX.  Cases for which $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{\rm s}} < 1$ are marked as `thermally unstable', as are cases for which the stagnation radius become very large and could not be resolved, resulting in their calculations being terminated.

Figure~\ref{fig:profiles} shows profiles of the density $\rho(r)$,
temperature $T(r)$, and radial velocity $|v(r)|$, for the cusp
($\Gamma=0.8$) solutions within our grid.  As expected, the gas
density increases towards the SMBH $\rho\propto r^{-n}$ with
$n\simeq1$, i.e. shallower than the $-3/2$ power law for
Bondi accretion. This power law behavior does not extend
through all radii, however, as the gas density profile has a break coincident
with the location of the break in the stellar light profile ($\rb=100$
pc). The temperature profile is relatively flat at large radii, but
increases as $\propto 1/r^{k}$ interior to the sphere of influence,
where $k\lesssim 1$, somewhat shallower than expected for virialized gas within the black hole sphere of influence.
The inwardly directed velocity increases towards the hole with a profile that is somewhat steeper than the local free-fall velocity $v \propto v_{\rm ff}\propto r^{-1/2}$.
% {\bf BDM: I made this up - in general we need
%   more explanation of what the plots are actually showing, with some
%   physical explanation.}
% AG -- things are not quite approaching Bondi on the inner grid. I
% don't have a good physical explanation yet...

Figure~\ref{fig:stag} shows our results for the stagnation radius $r_{\rm s}$, expressed in ratio to sphere of influence radius $r_{\rm soi}$, with different colors showing different values of $v_{w}$.  Cusp and core galaxies are marked with square and triangles, respectively.  Shown for comparison are our analytic results (eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core galaxies, respectively.  Our analytic estimates provide reasonably accurate fits to the numerical results for $v_{\rm w} \gtrsim \sigma$, but for low $v_{\rm w}$ they break down as the stagnation radius diverges to large radii.  For $v_{w} \gg \sigma$ the value $\rs/\rsoi$ does not depend sensitively on break radius $r_{b}$, but the latter has a greater influence when $v_{w} \lesssim \sigma$.  The three green squares located at the same value of $\vw =300 {\rm km/s}$, close to where the solid analytic line diverges, correspond to models with the same black hole masses $\Mbh = 10^7 \Msun=$ but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom).  
%% AG: Describe conservation checks to additionally validate the results.

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
    $r_{s}$ in units of the sphere of influence radius $r_{\rm
      soi}$ (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a
    function of the ratio of the effective wind heating rate $v_{w}$
    to the stellar velocity dispersion $\sigma$.  Green, orange, and
    blue symbols correspond to different values of $v_{w} =$ 300, 600, and 1200 km s$^{-1}$,
    respectively.  Squares correspond to cusp galaxies ($\Gamma = 0.8$), while
    triangles correspond to cores ($\Gamma = 0.1$). The black curves correspond to the
    analytic prediction from equation (\ref{eq:rs2main}), with solid and dashed curves calculated for parameters $\{\Gamma=0.8, n=1\}$ and $\{\Gamma=0.1,n=0.5\}$, respectively.  {\bf BDM: is the x axis here $v_{w}$ or $\vw$ !!?}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{cooling.eps}
  \caption{\label{fig:cooling} Ratio of the rate of heating to radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$, as a function of radius (solid lines) for each of our solutions shown in Figure \ref{fig:profiles}.  Dashed lines show for comparison the ratio of the cooling to the free-fall timescale $t_{\rm cool}/t_{\rm ff}$.  For high heating rates both ratios are approximately equal at the stagnation radius (marked as squares).  When $\dot{q}_{\rm heat}/\dot{q}_{\rm cool} \lesssim 1$ and/or $t_{\rm cool}/t_{\rm ff} \lesssim 10$, the flow is susceptible thermal instabilities.  {\bf BDM: change y axis labels to qdotheat/qdotcool, tcool/tff}.}
\end{figure}
